Analysis of Ontario Wildlife Hunting Data

### 2024-04-03 paper/paper.qmd
Simulated data for bears, deer, wolves, and moose

---
title: "Wildlife Hunting..."
author: Samantha Barfoot
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction

@@

# Results
 - Averages, means, etc (summary statistics)
 - Differences over time

@@

>>>>

---
title: "Analysis of Ontario Wildlife Hunting Data"
subtitle: "2009-2023"
author: Samantha Barfoot
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction

The analysis, graphs, and tables were made with [@citeR].

@@

# Results

@@

## What was done

## Something we learned about the world

## Another thing we learned about the world

## Weaknesses

## Looking forward
